---
title: "chronos_data_intro"
author: "Clara Suong"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: 
    toc: true # table of content true
    toc_depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: true  ## if you want number sections at each table header
    #theme: united  # many options for theme, this one is my favorite.
    highlight: tango  # specifies the syntax highlighting style
---
\newpage 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
knitr::opts_knit$set(root.dir = "/Users/clarahsuong/chronos_data_intro/")
#knitr::opts_knit$set(root.dir=rprojroot::find_rstudio_root_file("/Users/clarahsuong/chronos_data_intro/"))
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

#Load libraries and set the working directory
```{r, results='hide'}
rm(list = ls()) # clear objects in memory
library(plyr)
library(dplyr)
library(dbplyr)
library(tidyverse)
library(RMySQL) #For connecting to the databse
library(htmlTable) #For creating Word-compatible tables
library(lubridate) #For temporal variables
library(zoo) #For temporal variables
library(foreign)
library(ggplot2)
library(reshape2)
library(countrycode) #For reconciling different country codes across dataset
library(ISOcodes) #A package for ISO country codes
library(stargazer)
library(corrplot)
library(rowr) #For cbind with fill
library(gridExtra)
library(janitor)
```

#Databases and external datasets

##MySQL databases
* declassification_cables
* declassification_ddrs
* declassification_frus
* declassification_kissinger
* declassification_pdb
* declassification_clinton 
* declassification_cabinet
* declassification_cpdoc

##Key fields/variables in the database 'declassification_frus'
* body
* subject
* date (year)
* classification
* urgency
* length
* (handling)
* (page_count)
* (line_count)
* office
* from_field
* to_field
* tag

##Key fields/variables in the database 'declassification_cables'
* body
* subject
* date (year)
* classification
* urgency
* length
* (handling)
* (page_count)
* (line_count)
* office
* from_field
* to_field
* tag

##External dataset sources:
* Download the following datasets in the folder "external_data"
* COW country codes (cow): http://www.correlatesofwar.org/data-sets/cow-country-codes/cow-country-codes/at_download/file
* National Material Capabilities (v5.0) (nmc): http://www.correlatesofwar.org/data-sets/national-material-capabilities

#Data Overview

##List the collections
```{r}

setwd("/Users/clarahsuong/chronos_data_intro")

#Re-connect to the database
driver = dbDriver("MySQL")
connection = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader')
dbGetQuery(connection, 'show databases;')
```

##Download the table "docs" for all databases
```{r}

db_docs <- function(mydb) {
  mydb2 = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader', dbname=mydb)
  docs<-dplyr::tbl(mydb2, 'docs') %>% 
    collect(n = Inf) %>%
    distinct()
  return(docs)
}

#cables_docs<-db_docs('declassification_cables')
load("/Users/clarahsuong/Dropbox/nyu_postdoc/chronos_data_intro/raw_data/cables_docs.RData")
#cables_docs<-docs
load("/Users/clarahsuong/Dropbox/nyu_postdoc/chronos_data_intro/raw_data/frus_docs.RData")
#frus_docs<-db_docs('declassification_frus') 
clinton_docs<-db_docs('declassification_clinton') 
pdb_docs<-db_docs('declassification_pdb')
kissinger_docs<-db_docs('declassification_kissinger')
ddrs_docs<-db_docs('declassification_ddrs')
cabinet_docs<-db_docs('declassification_cabinet')
cpdoc_docs<-db_docs('declassification_cpdoc')
```

##Number of documents and date ranges for each collection
```{r}
db_doc_no_date <- function(mydb) {
mydb2<-eval(parse(text=paste(mydb, sep = "")), env=.GlobalEnv)
mydb2<-mydb2  %>%
  select(id, date) %>%
  collect() %>%
  distinct()
  
  return(c(nrow(mydb2), range(mydb2$date, na.rm = TRUE)))
}

db_doc_no_date('cables_docs')
db_doc_no_date('frus_docs')
db_doc_no_date('pdb_docs')
db_doc_no_date('kissinger_docs')
db_doc_no_date('clinton_docs') 
db_doc_no_date('ddrs_docs')
db_doc_no_date('cabinet_docs')
db_doc_no_date('cpdoc_docs')
```

##Frequency tables for full text vs. non-full text
```{r}

sum(!is.na(cables_docs$body))  
sum(!is.na(frus_docs$body))
sum(!is.na(pdb_docs$body))
sum(!is.na(kissinger_docs$body))
sum(!is.na(clinton_docs$body))
sum(is.na(ddrs_docs$body))
sum(!is.na(cabinet_docs$body))
sum(!is.na(cpdoc_docs$body))

sum(sum(!is.na(cables_docs$body)),
sum(!is.na(frus_docs$body)),
sum(!is.na(pdb_docs$body)),
sum(!is.na(kissinger_docs$body)),
sum(!is.na(clinton_docs$body)),
sum(is.na(ddrs_docs$body)),
sum(!is.na(cabinet_docs$body)),
sum(!is.na(cpdoc_docs$body))
)

sum(sum(!is.na(cables_docs$body)),
sum(!is.na(frus_docs$body)),
sum(!is.na(pdb_docs$body)),
sum(!is.na(kissinger_docs$body)),
sum(!is.na(clinton_docs$body)),
sum(is.na(ddrs_docs$body)),
sum(!is.na(cabinet_docs$body)),
sum(!is.na(cpdoc_docs$body))
)

sum(is.na(cables_docs$body))
sum(is.na(frus_docs$body))
sum(is.na(pdb_docs$body))
sum(is.na(kissinger_docs$body))
sum(is.na(clinton_docs$body))
sum(!is.na(ddrs_docs$body))
sum(is.na(cabinet_docs$body))
sum(is.na(cpdoc_docs$body))

sum(sum(is.na(cables_docs$body)),
sum(is.na(frus_docs$body)),
sum(is.na(pdb_docs$body)),
sum(is.na(kissinger_docs$body)),
sum(is.na(clinton_docs$body)),
sum(!is.na(ddrs_docs$body)),
sum(is.na(cabinet_docs$body)),
sum(is.na(cpdoc_docs$body))
)

sum(sum(is.na(cables_docs$body)),
sum(is.na(frus_docs$body)),
sum(is.na(pdb_docs$body)),
sum(is.na(kissinger_docs$body)),
sum(is.na(clinton_docs$body)),
sum(!is.na(ddrs_docs$body)),
sum(is.na(cabinet_docs$body)),
sum(is.na(cpdoc_docs$body)))
```

#CFPF Collection (declassification_cables)

##FIGURE: Bar Graph of Number of Cables by Month and Classification
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

cables_db = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader', dbname='declassification_cables')

classification_doc3 <- tbl(cables_db,'classification_doc') %>%
  collect() %>%
  distinct() %>%
  mutate(
    date=as_date(date), 
    month = as_date(cut(date, breaks = "month")),
    classification=ifelse(classification_id==1,"Secret",
                              ifelse(classification_id==2,"Confidential", 
                                     ifelse(classification_id==5,"Unclassified",
                                            ifelse(classification_id==7,"Limited Official Use", NA)
                                            )
                                    )
                              ),
    classification =factor(classification, levels = c("Unclassified", "Limited Official Use", "Confidential","Secret"))

        ) %>%
  select(classification, month) 

#png("./data_analysis_output/cables_n_month_class.png", width = 600, height = 450)
ggplot(classification_doc3, aes(month)) + 
  geom_bar(aes(fill=classification)) +
  scale_x_date(breaks=scales::pretty_breaks(10)) +
  scale_y_continuous(breaks=scales::pretty_breaks(10)) +
  labs(#title = "",
          #subtitle = "Data Plotted by Year",
           y = "Number of Documents",
           x = "Month") + 
  scale_fill_grey(start=0.8, end=0.2) +
  theme_bw() +
  theme(text = element_text(size=15),
        axis.text.x = element_text(size=11), 
        axis.text.y = element_text(size=11)#, 
        #legend.title=element_blank()#, 
        #legend.position = c(0.1, 0.9), 
        #legend.justification = c(0.1, 0.9)
        ) + labs(fill = "Classification")  
#scale_fill_manual(
#    values = cols,
#    aesthetics = c("colour","fill"),
#    breaks=c("Secret","Confidential","Limited Official Use","Unclassified")
#  ) 

#dev.off()
```

##Example Cable
```{r}
cables_db = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader', dbname='declassification_cables')

dbListTables(cables_db)

tbl(cables_db,'tag_doc') %>%
  filter(doc_id=="1976ECBRU06967")

tbl(cables_db,'tags') %>%
  filter(id==68 | id==88 | id==183)

tbl(cables_db,'country_doc') %>%
  filter(doc_id=="1976ECBRU06967")

#tbl(cables_db,'countries') %>%
#  filter(id==368)

tbl(cables_db,'topic_doc') %>%
  filter(topic_id==49) %>%
  collect() %>%
  arrange(desc(topic_score))

tbl(cables_db,'topic_doc') %>%
  filter(doc_id=="1976ECBRU06967")

# filter(doc_id=="1974ANKARA09370") 
#filter(doc_id=="1979HELSIN05792")
#filter(doc_id=="1977BONN09230")
#filter(doc_id=="1976DACCA06254")
#filter(doc_id=="1978OTTAWA02190")
#filter(doc_id=="1977TEHRAN01142")
#filter(doc_id=="1977TEHRAN01142")
#filter(doc_id=="1978BANGKO19143") 

tbl(cables_db,'topics') %>%
  filter(id==49 | id==30 | id==56)

topics<-tbl(cables_db,'topics') %>% collect()

#a<-tbl(cables_db,'topic_doc') %>%
#  group_by(doc_id) %>%
#  summarise(median = median(topic_score, na.rm = TRUE)) %>%
#  ungroup() %>%
#  arrange(desc(median)) %>%
#  collect()

topic_doc<-tbl(cables_db,'topic_doc') %>% collect()

a<-topic_doc %>%
  group_by(doc_id) %>%
  summarise(median = median(topic_score, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(median)) 

tbl(cables_db,'topic_doc') %>% arrange(desc(topic_score)) %>% print(n=40)
```

##Frequency Tables

###TABLE: Number of Documents with Non-Missing Values by Variable
```{r}
#driver = dbDriver("MySQL")
#connection = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader')
#mydb = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader', dbname='declassification_cables')

setwd("/Users/clarahsuong/chronos_data_intro")

docs<-
  cables_docs %>%
  dplyr::select("collection",
      "id",
      "body",
      "date",
      "classification",
      "subject", 
      "from_field", 
      "to_field", 
      #"tags",
      "concepts",
      "office",
      "handling",
      "type") 

C1<-c("collection",
      "id",
      "body",
      "date",
      "classification",
      "subject", 
      "from_field", 
      "to_field", 
      #"tags", 
      "concepts", 
      "office", 
      "handling", 
      "type")
  
C2<-c(
sum(!is.na(docs$collection)),
sum(!is.na(docs$id)),
sum(!is.na(docs$body)),
sum(!is.na(docs$date)),
sum(!is.na(docs$classification)),
sum(!is.na(docs$subject)),
sum(!is.na(docs$from_field)),
sum(!is.na(docs$to_field)),
sum(!is.na(docs$concepts)),
sum(!is.na(docs$office)),
sum(!is.na(docs$type))
)

table_cables_n_na<-cbind(C1, C2)
colnames(table_cables_n_na) <- c("Variable","Number of Documents with Non-Missing Values")

stargazer(table_cables_n_na,
          summary = FALSE,
          rownames = FALSE,
          type = "text", 
          title="Number of Documents with Non-Missing Values by Variable", 
          digits=1, 
          out="./data_analysis_output/table_cables_n_na.txt"
          )

#stargazer(table_cables_n_na,
#          summary = FALSE,
#          rownames = FALSE,
#          type = "html", 
#          title="Number of Documents with Non-Missing Values by Variable", 
#          digits=1, 
#          out="./data_analysis_output/table_cables_n_na.html"
#          )
```

###TABLE: Number of Cables by Year
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

table_cables_n_year<-
  cables_docs %>%
  mutate(year=lubridate::year(date)) %>%
  group_by(year) %>%
  tally() %>%
  mutate(total_n = sum(n),
        rel.freq = paste0(round(100 * n/total_n, 2), "%")) %>%
  select(year, n, rel.freq) %>%
  adorn_totals("row")

stargazer(table_cables_n_year[c("year","n", "rel.freq")],
          summary = FALSE,
          rownames = FALSE,
          type = "text", 
          title="Number of Cables By Year", 
          digits=1, 
          out="./data_analysis_output/table_cables_n_year.txt",
          covariate.labels=c("Year","Number of Cables", "Relative Frequency")
          )

#stargazer(table_cables_n_year[c("year","n", "rel.freq")],
#          summary = FALSE,
#          rownames = FALSE,
#          type = "html", 
#          title="Number of Cables By Year", 
#          digits=1, 
#          out="./data_analysis_output/table_cables_n_year.html",
#          covariate.labels=c("Year","Number of Cables", "Relative Frequency")
#          )
```

###TABLE: Number of Cables by Classification
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

#driver = dbDriver("MySQL")
#connection = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader')
cables_db = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader', dbname='declassification_cables')

classification_doc2 <- tbl(cables_db,'classification_doc') %>%
  collect() %>%
  distinct() %>%
  group_by(classification_id) %>% 
  tally() %>% 
  ungroup() %>% 
  mutate(total_n = sum(n),
        rel.freq = paste0(round(100 * n/total_n, 2), "%"),
        classification=ifelse(classification_id==1,"Secret",
                              ifelse(classification_id==2,"Confidential", 
                                     ifelse(classification_id==5,"Unclassified",
                                            ifelse(classification_id==7,"Limited Official Use", NA)
                                            )
                                    )
                              )
        ) %>%
  select(classification, n, rel.freq) %>%
  adorn_totals("row")

#classification_doc=apply_labels(classification_doc,
#                                classification_id="Classification",
#                                classification_id=num_lab("1 Secret
#                                                          2 Confidential
#                                                          7 Limited Official Use
#                                                          5 Unclassified")
#                                )

#table_classification = fre(classification_doc$classification_id) %>% 
#  set_caption("Table: Documents by Classification") %>%
#  htmlTable()

stargazer(classification_doc2[c("classification","n", "rel.freq")],
          summary = FALSE,
          rownames = FALSE,
          type = "text", 
          title="Number of Documents By Classification Level", 
          digits=1, 
          out="./data_analysis_output/table_cables_n_class.txt",
          covariate.labels=c("Classification","Number of Documents", "Relative Frequency"))

#stargazer(classification_doc2[c("classification","n", "rel.freq")],
#          summary = FALSE,
#          rownames = FALSE,
#          type = "html", 
#          title="Number of Documents By Classification Level", 
#          digits=1, 
#          out="./data_analysis_output/table_cables_n_class.html",
#          covariate.labels=c("Classification","Number of Documents", "Relative Frequency"))
```

#FRUS Collection

##FIGURE: Number of Documents by Year and Classification
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

frus_n_date<-
  frus_docs %>%
  dplyr::select(id, date, classification) %>%
  mutate(date=as_date(date), 
         Classification = replace_na(classification, "Missing"),
         year = as_date(cut(date, breaks = "year")),
         Classification =factor(Classification, levels = c("Missing", "Confidential","Secret","Top Secret")))

#cols <- c(
#          #"Confidential" =  
#            "#999999", 
#          #"Missing" = 
#            "#CCCCCC", 
#          #"Secret" = 
#          "#666666", 
#          #"Top Secret" = 
#          "#333333")

#png("./data_analysis_output/frus_n_year_class.png", width = 600, height = 450)
#layout(matrix(c(1:3), 3, 1,
# byrow = TRUE))
ggplot(frus_n_date, aes(year)) + 
  #geom_bar()
  geom_bar(aes(fill=Classification)) +
  scale_x_date(breaks=scales::pretty_breaks(10)) +
  scale_y_continuous(breaks=scales::pretty_breaks(10)) +
  labs(#title = "",
          #subtitle = "Data Plotted by Year",
           y = "Number of Documents",
           x = "Year") + 
#  scale_fill_manual(
#    values = cols,
#    aesthetics = c("colour","fill"),
#    breaks=c("Top Secret","Secret","Confidential","Missing")
#  ) +
  theme_bw() +
  theme(text = element_text(size=15),
        axis.text.x = element_text(size=11), 
        axis.text.y = element_text(size=11), 
        #legend.title=element_blank(), 
        legend.position = c(0.1, 0.9), 
        legend.justification = c(0.1, 0.9))   +
  scale_fill_grey(start=0.8, end=0.2) #+
#  scale_fill_discrete(breaks=c("Missing","Confidential","Secret","Top Secret"))
#dev.off()
```

##Example Document
```{r}
#driver = dbDriver("MySQL")
#connection = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader')
frus_db = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader', dbname='declassification_frus')

dbListTables(frus_db)

tbl(frus_db,'country_doc') %>%
  filter(doc_id=="frus1945v02d128")

tbl(frus_db,'countries') %>%
  filter(id==156 | id==250)

tbl(frus_db,'topic_doc') %>%
  filter(doc_id=="frus1945v02d128")

tbl(frus_db,'topics') %>% #Replace with 'curated_topics' later.
  filter(id==1059 | id==1062 | id==1069)

a<-frus_docs %>%
  filter(id=="frus1945v02d128") 
```

##Frequency Tables 

###TABLE: Number of Documents with Non-Missing Values by Variable
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

C1<-c("collection",
      "id",
      "body",
      "date",
      "classification",
      "volume_id",
      "chapt_title",
      "title", 
      #"subject",
      #"location", 
      "p_from",
      "p_to",
      "source"
)
  
C2<-c(sum(!is.na(frus_docs$collection)),
sum(!is.na(frus_docs$id)),
sum(!is.na(frus_docs$body)),
sum(!is.na(frus_docs$date)),
sum(!is.na(frus_docs$classification)),
sum(!is.na(frus_docs$volume_id)),
sum(!is.na(frus_docs$chapt_title)),
sum(!is.na(frus_docs$title)),
sum(!is.na(frus_docs$p_from)),
sum(!is.na(frus_docs$p_to)),
sum(!is.na(frus_docs$source))
)

table_frus_n_na<-cbind(C1, C2)
colnames(table_frus_n_na) <- c("Variable","Number of Documents with Non-Missing Values")

#htmlTable(ns,  
#          ctable=c("solid", "double"),
#          caption="Number of Documents with Non-Missing Values")

stargazer(table_frus_n_na,
          summary = FALSE,
          rownames = FALSE,
          type = "text", 
          title="Number of Documents with Non-Missing Values by Variable", 
          digits=1, 
          out="./data_analysis_output/table_frus_n_na.txt"
          )

#stargazer(table_frus_n_na,
#          summary = FALSE,
#          rownames = FALSE,
#          type = "html", 
#          title="Number of Documents with Non-Missing Values by Variable", 
#          digits=1, 
#          out="./data_analysis_output/table_frus_n_na.html"
#          )
```

###TABLE: Number of Documents by Year
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

table_frus_n_year<-
  frus_docs %>%
  mutate(year=lubridate::year(date)) %>%
  group_by(year) %>%
  tally() %>%
  mutate(total_n = sum(n),
        rel.freq = paste0(round(100 * n/total_n, 2), "%")) %>%
  ungroup() %>% 
  adorn_totals("row")

stargazer(table_frus_n_year[c("year","n", "rel.freq")],
          summary = FALSE,
          rownames = FALSE,
          type = "text", 
          title="Number of Documents By Year", 
          digits=1, 
          out="./data_analysis_output/table_frus_n_year.txt",
          covariate.labels=c("Year","Number of Documents", "Relative Frequency")
          )

#stargazer(table_frus_n_year[c("year","n", "rel.freq")],
#          summary = FALSE,
#          rownames = FALSE,
#          type = "html", 
#          title="Number of Documents By Year", 
#          digits=1, 
#          out="./data_analysis_output/table_frus_n_year.html",
#          covariate.labels=c("Year","Number of Documents", "Relative Frequency")
#          )
```

###TABLE: Number of Documents by Classification
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

table_frus_n_class<-
  frus_docs %>%
  mutate(year=lubridate::year(date)) %>%
  group_by(classification) %>%
  tally() %>%
  mutate(total_n = sum(n),
        rel.freq = paste0(round(100 * n/total_n, 2), "%")) %>%
  ungroup() %>% 
  adorn_totals("row")

stargazer(table_frus_n_class[c("classification","n", "rel.freq")],
          summary = FALSE,
          rownames = FALSE,
          type = "text", 
          title="Number of Documents By Classification Level", 
          digits=1, 
          out="./data_analysis_output/table_frus_n_class.txt",
          covariate.labels=c("Classification","Number of Documents", "Relative Frequency"))

#stargazer(table_frus_n_class[c("classification","n", "rel.freq")],
#          summary = FALSE,
#          rownames = FALSE,
#          type = "html", 
#          title="Number of Documents By Classification Level", 
#          digits=1, 
#          out="./data_analysis_output/table_frus_n_class.html",
#          covariate.labels=c("Classification","Number of Documents", "Relative Frequency"))
```

#Country TAG Traffic

##Examine the different country codes across datasets
```{r}

setwd("/Users/clarahsuong/chronos_data_intro")

#Re-connect to the database
driver = dbDriver("MySQL")
connection = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader')
mydb = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader', dbname='declassification_cables')

#A list of countries according to our database
countries<-
  tbl(mydb, 'countries') %>% 
  collect() 
#This table is incomplete. Note that there is no tag for "South Vietnam" but tag "VM" (id: 557) for "Vietnam" according to this table. The 1976 TAGS manual lists VN (tag_id=1976) for "Viet-Nam (North)"and VS (tag_id=1973) for "Viet-Nam (South)". There is also no tag_id and 2 country_ids for Ethiopia. 
#US is included.
#Note there is no tag_id for the Soviet Union but one for Russia.

#Merge ISO_3166_1 and ISO_3166_3 (ISO country codes for withdrawn countries). Note that this list often omits retired codes. 
iso_3166<-
  tibble::as_tibble(full_join(ISO_3166_1, ISO_3166_3, by = c("Alpha_3","Numeric","Name")))%>%
  mutate(Numeric=as.integer(Numeric)) %>%
  dplyr::select("Alpha_3",
         "Numeric",
         "Name",
         "Official_name",
         "Common_name") 

#Generate a dataframe for all (former and existing) countries according to COW. Note that this includes the US.
all_states<-
  read_csv("./external_data/cow/states2016.csv") %>%
  dplyr::select("stateabb","ccode","statenme") %>%
  #filter(!ccode==2) %>% #Leave out the US
  rename(cow_ccode=ccode,
         cow_stateabb=stateabb, 
         cow_statename=statenme) %>%   
  mutate(cow_stateabb=as.character(cow_stateabb),
         cow_statename=as.character(cow_statename)) %>%
  distinct() #There are duplicates. e.g. countries that existed, disappeared, and then re-appeared. Serbia is also not on the list.

#Generate a dataframe for all (former and existing) countries for years 1973-79. Note that this includes the US.
all_states_year<-
  all_states %>%
  rowr::cbind.fill(c(1973:1979),fill = NA) %>%
  rename(year=object) %>%
  expand(year = 1973:1979, nesting(cow_stateabb, 
                                   cow_ccode,                    
                                   cow_statename))

#Generate a dataframe for countries existing during the period of 1973-79. Note that the universe of countries differs by year due to the difference in countries' birth/death years. Note that this also includes the US.
states_70s_year<-
  read_csv("./external_data/cow/system2016.csv") %>%
  dplyr::select("stateabb","ccode","year") %>%
  filter(year>1972 & year<1980) %>%
  rename(cow_ccode=ccode, 
         cow_stateabb=stateabb) %>%
  left_join(all_states, by=c("cow_ccode","cow_stateabb")) #Include COW state names.

states_70s<-
  states_70s_year %>%
  dplyr::select(-year) %>%
  distinct() 
```

##Create a dataframe linking country codes and tag_ids
```{r}
#Re-connect to the database
driver = dbDriver("MySQL")
connection = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader')
mydb = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader', dbname='declassification_cables')

#Note that this includes country codes and tag_id for the US.
country_code_tag<-
  tbl(mydb, 'countries') %>% 
  collect() %>%
  mutate(country_id=as.integer(id)) %>%
  dplyr::select(-id) %>%
  mutate(cow_ccode=countrycode(name, 'country.name', 'cown')) %>% #Derive COW country codes from the variable "name" in the table "countries."
  mutate(iso3n=countrycode(name, 'country.name', 'iso3n')) #Derive iso numeric country codes from the variable "name" in the table "countries."
  
#Check whether the variable "country_id" in the table "countries" is from ISO 3166.
#cow_ccode for Vietnam should be 816, not 817 (error in the package countrycode) and cow_ccode for West Germany (German Federal Republic) should be 260.
#iso3n for South Vietnam should not be 704 (country code of Vietnam) but 714 (error in the R package countrycode). The tag_id for South Vietnam is missing. There are two country ids and only one tag_id for Ethiopia.
#country_code_tag$cowid2<-countrycode(country_code_tag$country_id, 'iso3n', 'cown')

all(country_code_tag$country_id %in% iso_3166$Numeric)
all(iso_3166$Numeric %in% country_code_tag$country_id)
setdiff(country_code_tag$country_id, iso_3166$Numeric)
country_code_tag[country_code_tag$country_id %in% setdiff(country_code_tag$country_id, iso_3166$Numeric),]
#Most of the items with a discrepancy between the database's country_id and iso-3166 numeric seem to be defunct states or non-state entities, except East and West Germany.

#Replace the wrong COW country codes and tag_id
country_code_tag<-
  country_code_tag %>%
  mutate(cow_ccode= replace(cow_ccode, name=="Vietnam", 816), #Fix cow_ccode for Vietnam 
         cow_ccode= replace(cow_ccode, name=="West Germany", 260), #Fix cow_ccode for West Germany (German Federal Republic) 
         tag_id=replace(tag_id, name=="South Vietnam", 1973), #Insert tag_id for South Vietnam
         tag_id=replace(tag_id, name=="Ethiopia", 405),
         country_id=replace(country_id, name=="Ethiopia", 231)) %>% #Insert tag_id for South Vietnam
  rbind(c("Vietnam",
          0,
          1,
          1976,
          704,
          816,
          704
          )
        ) %>% #Insert the second tag_id value (1976) for Vietnam 
  filter(!(name=="Panama" & country_id==590)) %>%
  mutate(cow_ccode=as.integer(cow_ccode),
         tag_id=as.integer(tag_id)) %>%
  right_join(all_states, by="cow_ccode") %>% #Include state names from the COW list of all states that have ever existed.
  rename(country_name=name) %>% 
  #filter(!is.na(cow_ccode) & !is.na(tag_id)) %>% #Drop the observations with missing COW country code and missing tag_id.
  dplyr::select(-iso3n, -country_name,-deleted,-official) %>% #Note the 2 tags for Vietnam.
  distinct()

```

##Tag traffic by country-year and by country

###Download, save, or load the tables for tags and docs (doc_id and date) in the working directory and count the number of cables tagged for each country
```{r results='hide'}

setwd("/Users/clarahsuong/chronos_data_intro")

#Re-connect to the database
driver = dbDriver("MySQL")
connection = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader')
mydb = dbConnect(driver,host='history-lab.org', password='XreadF403', user='de_reader', dbname='declassification_cables')

tags<-
  tbl(mydb, 'tags') %>% 
  dplyr::select(id, tag, category) %>% 
  collect() 

tag_doc<-
  tbl(mydb, 'tag_doc') %>% 
  collect() #This table includes cables tagged with South Vietnam (tag_id 1973) and Vietnam (tag_id: 1976 and 557)
#tag_doc %>% filter(tag_id==1973)
#tag_doc %>% filter(tag_id==1976)
#tag_doc %>% filter(tag_id==557)

doc_date2<-
  tbl(mydb, 'docs') %>% 
  dplyr::select(id, date) %>%
  rename(doc_id=id) %>% 
  collect()

country_tag_doc2<-
  tag_doc %>%
  inner_join(doc_date2, by = "doc_id") %>%
  inner_join(tags, by = c("tag_id"="id")) %>%
  inner_join(country_code_tag, by="tag_id") %>%
  mutate(year=lubridate::year(date), 
         month=lubridate::month(date), 
         date=lubridate::ymd(date), 
         ym=as.yearmon(paste(year, month),"%Y %m")
         ) 
save(country_tag_doc2, file = "./data/country_tag_doc2.RData")
#load("./data/country_tag_doc2.RData")

cable_n_day<-
  country_tag_doc2 %>%
  group_by(.dots=c("cow_ccode", 
                   "cow_statename",
                   "country_id", 
                   "date")) %>%
  tally() %>%
  ungroup()
save(cable_n_day, file = "./data/cable_n_day.RData")
#load("./data/cable_n_day.RData") #Note that this includes neither all dates nor all countries on the COW list.

#The table country_doc attempts to add West Germany and South Vietnam based on regex matching in body.
#country_doc<-
#  tbl(mydb, 'country_doc') %>% collect()
#However, this table is also missing South Vietnam (country_id 714 or tag_id 1973). It seems to group (North) Vietnam and South Vietnam together, probably as a result of directly extracting Vietnam from the documents. The search in the table said there are 15,668 documents related to or tagged with Vietnam. 
#country_doc %>% filter(country_id==714)
#country_doc %>% filter(country_id==704)
#It is meaningful to distinguish cables related to South Vietnam from those about (North) Vietnam. Thus, do not use this table.

#Yearly tag traffic by state-year, including 0 cables by some countries that did not exist in the 1970s. Note that this does include the cables tagged with US. 
cable_n_all_states_year<-
  country_tag_doc2 %>%
  group_by(year, cow_ccode, cow_statename, cow_stateabb) %>%
  tally() %>%
  right_join(all_states_year, by=c("year", "cow_ccode", "cow_stateabb","cow_statename")) %>%
  rename(n_c_y=n) %>%
  mutate(n_c_y= replace(n_c_y, is.na(n_c_y), 0)) %>%
  ungroup() %>%
  mutate(total_n = sum(n_c_y)) %>%
  arrange(year, cow_ccode)
#save(cable_n_all_states_year, file = "./data/cable_n_all_states_year.RData")
#load("./data/cable_n_all_states_year.RData")

#Tag traffic by state, including 0 cables by some countries that did not exist in the 1970s. Note that this does include the cables tagged with US. 
cable_n_all_states<-
  country_tag_doc2 %>%
  group_by(cow_ccode, cow_statename, cow_stateabb) %>%
  tally() %>%
  right_join(all_states, by=c("cow_ccode", "cow_stateabb","cow_statename")) %>%
  rename(n_c=n) %>%
  mutate(n_c= replace(n_c, is.na(n_c), 0)) %>%
  ungroup() %>%
  mutate(total_n = sum(n_c)) %>%
  arrange(desc(n_c))
#save(cable_n_all_states, file = "./data/cable_n_all_states.RData")
#load("./data/cable_n_all_states.RData")

#Yearly tag traffic by state-year, excluding 0 cables by some countries that did not exist in the 1970s. Note that this does include the cables tagged with US. 
cable_n_states_70s_year<-
  country_tag_doc2 %>%
  group_by(year, cow_ccode, cow_statename, cow_stateabb) %>%
  tally() %>%
  right_join(states_70s_year, by=c("year", "cow_ccode", "cow_stateabb","cow_statename")) %>%
  rename(n_c_y=n) %>%
  mutate(n_c_y= replace(n_c_y, is.na(n_c_y), 0)) %>%
  ungroup() %>%
  mutate(total_n = sum(n_c_y)) %>%
  arrange(year, cow_ccode)
#save(cable_n_states_70s_year, file = "./data/cable_n_states_70s_year.RData")
#load("/Users/clarahsuong/chronos_data_intro/data/cable_n_states_70s_year.RData")

#Tag traffic by state, excluding 0 cables by some countries that did not exist in the 1970s. Note that this does include the cables tagged with US. 
cable_n_states_70s<-
  country_tag_doc2 %>%
  group_by(cow_ccode, cow_statename, cow_stateabb) %>%
  tally() %>%
  right_join(states_70s, by=c("cow_ccode", "cow_stateabb","cow_statename")) %>%
  rename(n_c=n) %>%
  mutate(n_c= replace(n_c, is.na(n_c), 0)) %>%
  ungroup() %>%
  mutate(total_n = sum(n_c)) %>%
  arrange(desc(n_c))
#save(cable_n_states_70s, file = "./data/cable_n_states_70s.RData")
#load("/Users/clarahsuong/chronos_data_intro/data/cable_n_states_70s.RData")

#Note that the total ns for each dataset for differs a bit.
```

###TABLE: Summary Statistics of Country TAG Traffic by Country-Year (Only Contemporary Non-US Countries)
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

stargazer(as.data.frame(cable_n_states_70s_year[cable_n_states_70s_year$cow_ccode!=2,])[c("year", "cow_ccode", "n_c_y")], 
          type = "text", 
          title="Summary Statistics of Tag Traffic by Country-Year (Only Contemporary Non-US Countries)", 
          digits=1, 
          out="./data_analysis_output/desc_cable_n_nonus_states_70s_year.txt",
          covariate.labels=c("Year", "COW Codes of Countries", "Country TAG Traffic"))


#stargazer(as.data.frame(cable_n_states_70s_year[cable_n_states_70s_year$cow_ccode!=2,])[c("year", "cow_ccode", "n_c_y")], 
#          type = "html", 
#          title="Summary Statistics of Tag Traffic by Country-Year (Only Contemporary Non-US Countries)", 
#          digits=1, 
#          out="./data_analysis_output/desc_cable_n_nonus_states_70s_year.html",
#          covariate.labels=c("Year", "COW Codes of Countries", "Country TAG Traffic"))
```

###TABLE: Summary Statistics of Country TAG Traffic by Country (Only Contemporary Non-US Countries) 
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

stargazer(as.data.frame(cable_n_states_70s[cable_n_states_70s$cow_ccode!=2,])[c("cow_ccode", "n_c")], 
          type = "text", 
          title="Summary Statistics of Tag Traffic by Country (Only Contemporary Non-US Countries)", 
          digits=1, 
          out="./data_analysis_output/desc_cable_n_nonus_states_70s.txt",
          covariate.labels=c("COW Codes of Countries", "Country TAG Traffic"))

#stargazer(as.data.frame(cable_n_states_70s[cable_n_states_70s$cow_ccode!=2,])[c("cow_ccode", "n_c")],
#          type = "html", 
#          title="Summary Statistics of Tag Traffic by Country (Only Contemporary Non-US Countries)",
#          digits=1, 
#          out="./data_analysis_output/desc_cable_n_nonus_states_70s.html",
#          covariate.labels=c("COW Codes of Countries", "Country TAG Traffic"))
```

###FIGURE: Country TAG Traffic at Country-Year and Country Levels
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

options(scipen=10000000)

p1<-ggplot(cable_n_states_70s_year[cable_n_states_70s_year$cow_ccode!=2,], aes(n_c_y)) +
  #geom_freqpoly(bins = 300) +
  geom_histogram(bins = 300) +
  theme_bw() +
  labs(title = "By Country-Year",
       #subtitle = "Data Plotted by Year",
    y = "Count",
    x = "Country TAG Traffic"
    ) + 
    theme(text = element_text(size=12),
        axis.text.x = element_text(size=11), 
        axis.text.y = element_text(size=11)#, 
        #legend.title=element_blank()#, 
        #legend.position = c(0.1, 0.9), 
        #legend.justification = c(0.1, 0.9)
        )

p2<-ggplot(cable_n_states_70s[cable_n_states_70s$cow_ccode!=2,], aes(n_c)) +
  geom_histogram(bins = 300) +
  #  geom_freqpoly(bins = 300) +
  theme_bw() +
  labs(title = "By Country",
       #subtitle = "Data Plotted by Year",
    y = "Count",
    x = "Country TAG Traffic") + 
    theme(text = element_text(size=12),
        axis.text.x = element_text(size=11), 
        axis.text.y = element_text(size=11)#, 
        #legend.title=element_blank()#, 
        #legend.position = c(0.1, 0.9), 
        #legend.justification = c(0.1, 0.9)
        ) +
    xlim(0, 151000)

#png("./data_analysis_output/cable_n_nonus_states_70s_year_freq.png")
grid.arrange(p1, p2)
#dev.off()
```
###Percentile for Specific Values
```{r}
ecdf_fun <- function(x,perc) ecdf(x)(perc)
ecdf_fun(cable_n_states_70s_year[cable_n_states_70s_year$cow_ccode!=2,]$n_c_y,5000)
ecdf_fun(cable_n_states_70s_year[cable_n_states_70s_year$cow_ccode!=2,]$n_c_y,10000)-ecdf_fun(cable_n_states_70s_year[cable_n_states_70s_year$cow_ccode!=2,]$n_c_y,5000)
1-ecdf_fun(cable_n_states_70s_year[cable_n_states_70s_year$cow_ccode!=2,]$n_c_y,10000)

ecdf_fun(cable_n_states_70s[cable_n_states_70s$cow_ccode!=2,]$n_c,25000)
ecdf_fun(cable_n_states_70s[cable_n_states_70s$cow_ccode!=2,]$n_c,75000)-ecdf_fun(cable_n_states_70s[cable_n_states_70s$cow_ccode!=2,]$n_c,25000)
1-ecdf_fun(cable_n_states_70s[cable_n_states_70s$cow_ccode!=2,]$n_c,75000)
```

###TABLE: Summary Statistics of Country TAG Traffic by Country-Year (Including Former Countries and the US)
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

stargazer(as.data.frame(cable_n_all_states_year)[c("year", "cow_ccode", "n_c_y")], 
          type = "text", 
          title="Summary Statistics of Country TAG Traffic by Country-Year (Incl. Former Countries and the US)", 
          digits=1, 
          out="./data_analysis_output/desc_cable_n_all_states_year.txt",
          covariate.labels=c("Year", "COW Codes of Countries", "Country TAG Traffic"))

#stargazer(as.data.frame(cable_n_all_states_year)[c("year", "cow_ccode", "n_c_y")], 
#          type = "html", 
#          title="Summary Statistics of Country TAG Traffic by Country-Year (Incl. Former Countries and the US)", 
#          digits=1, 
#          out="./data_analysis_output/desc_cable_n_all_states_year.html",
#          covariate.labels=c("Year", "COW Codes of Countries", "Country TAG Traffic"))
```

###TABLE: Summary Statistics of Country TAG Traffic by Country (Incl. Former Countries and the US)
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

stargazer(as.data.frame(cable_n_all_states)[c("cow_ccode", "n_c")], 
          type = "text", 
          title="Summary Statistics of Country TAG Traffic by Country (Incl. Former Countries and the US)", 
          digits=1, 
          out="./data_analysis_output/desc_cable_n_all_states.txt",
          covariate.labels=c("COW Codes of Countries", "Country TAG Traffic"))

#stargazer(as.data.frame(cable_n_all_states)[c("cow_ccode", "n_c")], 
#          type = "html", 
#          title="Summary Statistics of Country TAG Traffic by Country (Incl. Former Countries and the US)", 
#          digits=1, 
#          out="./data_analysis_output/desc_cable_n_all_states.html",
#          covariate.labels=c("COW Codes of Countries", "Country TAG Traffic"))
```

###FIGURE: Country TAG Traffic at Country-Year and Country Levels (All Countries)
```{r}
options(scipen=10000000)

p3<-
  ggplot(cable_n_all_states_year, aes(n_c_y)) +
# geom_histogram(bins = 300) + 
  geom_freqpoly(bins = 300) +
  theme_bw() +
  labs(title = "By Country-Year",
       #subtitle = "Data Plotted by Year",
    y = "Frequency",
    x = "Country TAG Traffic") + 
    theme(text = element_text(size=15),
        axis.text.x = element_text(size=11), 
        axis.text.y = element_text(size=11)#, 
        #legend.title=element_blank()#, 
        #legend.position = c(0.1, 0.9), 
        #legend.justification = c(0.1, 0.9)
        )

p4<-
  ggplot(cable_n_all_states, aes(n_c)) +
# geom_histogram(bins = 300) + 
  geom_freqpoly(bins = 300) +
  theme_bw() +
  labs(title = "By Country",
       #subtitle = "Data Plotted by Year",
    y = "Frequency",
    x = "Country TAG Traffic") + 
    theme(text = element_text(size=15),
        axis.text.x = element_text(size=11), 
        axis.text.y = element_text(size=11)#, 
        #legend.title=element_blank()#, 
        #legend.position = c(0.1, 0.9), 
        #legend.justification = c(0.1, 0.9)
        )

#png("./data_analysis_output/cable_n_all_states_year_freq.png")
grid.arrange(p3, p4)
#dev.off()
```

###TABLE: Country TAG Traffic vs. Cable Traffic
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

russia_cable_traffic_1<-
  cables_docs %>% 
  filter(str_detect(to_field, "MOSCOW") |
         str_detect(to_field, "LENINGRAD") |  
         str_detect(from_field, "MOSCOW") |  
         str_detect(from_field, "LENINGRAD")) %>% 
  mutate(year=lubridate::year(date)) %>%
  group_by(year) %>%
  tally()

russia_cable_traffic_2<-
  cables_docs %>% 
  filter(str_detect(to_field, "MOSCOW") |
         #str_detect(to_field, "LENINGRAD") |  
         str_detect(from_field, "MOSCOW") #|  
         #str_detect(from_field, "LENINGRAD")
           )%>% 
  mutate(year=lubridate::year(date)) %>%
  group_by(year) %>%
  tally()

russia_cable_traffic_3<-
  cables_docs %>% 
  filter(#str_detect(to_field, "MOSCOW") |
         str_detect(to_field, "LENINGRAD") |  
         #str_detect(from_field, "MOSCOW") |  
         str_detect(from_field, "LENINGRAD")
           )%>% 
  mutate(year=lubridate::year(date)) %>%
  group_by(year) %>%
  tally()

russia_tag<-
  cable_n_states_70s_year %>%
  filter(cow_statename=="Russia")

russia_tag_cable_traffic<-cbind(russia_tag[c("year", "n_c_y")], 
                                #russia_cable_traffic_1["n"],
                                russia_cable_traffic_2["n"],
                                russia_cable_traffic_3["n"]
                                )

#colnames(russia_tag_cable_traffic) <- c("Year","Country TAG Traffic", "Cable Traffic")

stargazer(russia_tag_cable_traffic,
          type = "text", 
          #flip = TRUE,
          summary = FALSE,
          rownames = FALSE,
          title="Comparison of Country TAG Traffic and Cable Traffic", 
          digits=1, 
          out="./data_analysis_output/russia_tag_cable_traffic.txt",
          covariate.labels=c("Year", 
                             "Number of Cables Tagged<br>with the USSR", 
                             #"Number of Cables Sent by/to<br>the US Embassy in Moscow<br>and the Consulate General in Leningrad", 
                             "Number of Cables Sent by/to<br>the US Embassy in Moscow",
                             "Number of Cables Sent by/to<br>the US Consulate General in Leningrad")
          )

#stargazer(russia_tag_cable_traffic,
#          type = "html", 
#          summary = FALSE,
#          rownames = FALSE,
#          title="Comparison of Country TAG Traffic and Cable Traffic", 
#          digits=1, 
#          out="./data_analysis_output/russia_tag_cable_traffic.html",
#          covariate.labels=c("Year", 
#                             "Number of Cables Tagged with the USSR", 
#                             #"Number of Cables Sent by/to<br>the US Embassy in Moscow<br>and the Consulate General in Leningrad", 
#                             "Number of Cables Sent by/to the US Embassy in Moscow",
#                             "Number of Cables Sent by/to< the US Consulate General in Leningrad")
#          )
```

###Country TAG Traffic for Certain Countries
```{r, echo=FALSE}
#Check tag_id 
#country_code_tag%>%filter(str_detect(country_name, 'Germany'))
#country_code_tag%>%filter(str_detect(country_name, 'Viet'))
#country_code_tag%>%filter(str_detect(country_name, 'Rhodesia'))

cable_east_germany<-
  country_tag_doc2 %>%
  filter(tag_id==419 & (year==1973 | year==1974)) %>%
  group_by(year) %>%
  tally() 
cable_east_germany

cable_viet<-
  country_tag_doc2 %>%
  filter((tag_id==557 | tag_id==1976) & year>1973) %>%
  group_by(year) %>%
  tally() 
cable_viet

cable_rhodesia<-
  country_tag_doc2 %>%
  filter(tag_id==508 & year==1978) %>%
  group_by(year) %>%
  tally()
cable_rhodesia
```

###TABLE: Non-US Country-Years with Most Cables
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

table_tag_state_year_top20<- 
  cable_n_states_70s_year %>%
  filter(cow_ccode!=2) %>%
  mutate(rel.freq = paste0(round(100 * n_c_y/total_n, 2), "%")) %>%
  arrange(desc(n_c_y)) %>%
  top_n(n = 20, wt = n_c_y) %>%
  mutate(cow_statename= replace(cow_statename, cow_statename=="Russia", "Soviet Union")) #Replace "Russia" with "Soviet Union"

stargazer(table_tag_state_year_top20[c("year", "cow_statename", "n_c_y","rel.freq")],
          summary = FALSE,
          rownames = FALSE,
          type = "text", 
          title="Non-US Country-Years with Highest Tag Traffic", 
          digits=1, 
          out="./data_analysis_output/table_tag_state_year_top20.txt",
          covariate.labels=c("Year","Tagged Country", "Number of Cables", "Relative Frequency"))


#stargazer(table_tag_state_year_top20[c("year", "cow_statename", "n_c_y","rel.freq")],
#          summary = FALSE,
#          rownames = FALSE,
#          type = "html", 
#          title="Non-US Country-Years with Highest Tag Traffic", 
#          digits=1, 
#          out="./data_analysis_output/table_tag_state_year_top20.html",
#          covariate.labels=c("Year","Tagged Country", "Number of Cables", "Relative Frequency"))
```

###TABLE: Non-US Country-Years Tagged in Fewest Cables
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

table_tag_state_year_bottom20<- 
  cable_n_states_70s_year %>%
  filter(cow_ccode!=2) %>%
  mutate(rel.freq = paste0(round(100 * n_c_y/total_n, 2), "%")) %>%
  arrange(desc(n_c_y)) %>%
  top_n(n = -20, wt = n_c_y) %>%
  mutate(cow_statename= replace(cow_statename, cow_statename=="Russia", "Soviet Union")) #Replace "Russia" with "Soviet Union"


stargazer(table_tag_state_year_bottom20[c("year", "cow_statename", "n_c_y","rel.freq")],
          summary = FALSE,
          rownames = FALSE,
          type = "text", 
          title="Non-US Country-Years with Lowest Tag Traffic", 
          out="./data_analysis_output/table_tag_state_year_bottom20.txt",
          covariate.labels=c("Year","Tagged Country", "Number of Cables", "Relative Frequency"))

#stargazer(table_tag_state_year_bottom20[c("year", "cow_statename", "n_c_y","rel.freq")],
#          summary = FALSE,
#          rownames = FALSE,
#          type = "html", 
#          title="Non-US Country-Years with Lowest Tag Traffic", 
#          out="./data_analysis_output/table_tag_state_year_bottom20.html",
#          covariate.labels=c("Year","Tagged Country", "Number of Cables", "Relative Frequency"))
```


###TABLE: Countries Most Frequently Tagged in Cables
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

table_tag_state_top20<- 
  cable_n_states_70s %>%
  filter(cow_ccode!=2) %>%
  #group_by(cow_ccode, cow_stateabb, cow_statename) %>% 
  #summarise(n_c = sum(n_c)) %>%
  #ungroup %>%
  mutate(rel.freq = paste0(round(100 * n_c/total_n, 2), "%")) %>%
  arrange(desc(n_c)) %>%
  top_n(n = 20, wt = n_c) %>%
  mutate(cow_statename= replace(cow_statename, cow_statename=="Russia", "Soviet Union")) #Replace "Russia" with "Soviet Union"

stargazer(table_tag_state_top20[c("cow_statename", "n_c","rel.freq")],
          summary = FALSE,
          rownames = FALSE,
          type = "text", 
          title="Non-US Countries Most Frequently Tagged in Cables", 
          out="./data_analysis_output/table_tag_state_top20.txt",
          covariate.labels=c("Country", "Number of Cables", "Relative Frequency"))

#stargazer(table_tag_state_top20[c("cow_statename", "n_c","rel.freq")],
#          summary = FALSE,
#          rownames = FALSE,
#          type = "html", 
#          title="Non-US Countries Most Frequently Tagged in Cables", 
#          out="./data_analysis_output/table_tag_state_top20.html",
#          covariate.labels=c("Country", "Number of Cables", "Relative Frequency"))
```

###TABLE: Non-U.S. Countries Least Frequently Tagged in Cables
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

table_tag_state_bottom20<- 
  cable_n_states_70s %>%
  filter(cow_ccode!=2) %>%
  mutate(rel.freq = paste0(round(100 * n_c/total_n, 0), "%")) %>%
  arrange(desc(n_c)) %>%
  top_n(n = -20, wt = n_c) %>%
  mutate(cow_statename= replace(cow_statename, cow_statename=="Russia", "Soviet Union")) #Replace "Russia" with "Soviet Union"

stargazer(table_tag_state_bottom20[c("cow_statename", "n_c","rel.freq")],
          summary = FALSE,
          rownames = FALSE,
          type = "text", 
          title="Non-US Countries Least Frequently Tagged in Cables", 
          digits=1, 
          out="./data_analysis_output/table_tag_state_bottom20.txt",
          covariate.labels=c("Country", "Number of Cables", "Relative Frequency"))

#stargazer(table_tag_state_bottom20[c("cow_statename", "n_c","rel.freq")],
#          summary = FALSE,
#          rownames = FALSE,
#          type = "html", 
#          title="Non-US Countries Least Frequently Tagged in Cables", 
#          digits=1, 
#          out="./data_analysis_output/table_tag_state_bottom20.html",
#          covariate.labels=c("Country", "Number of Cables", "Relative Frequency"))
```

###TABLE: Country TAG Traffic vs. Total Population
```{r}
setwd("/Users/clarahsuong/chronos_data_intro")

nmc_c_y<-
  read_csv("./external_data/NMC_5_0/NMC_5_0.csv") %>%
  dplyr::select("stateabb", "ccode", "year","tpop") 

pop_c <- 
  read_csv("./external_data/NMC_5_0/NMC_5_0.csv") %>%
  dplyr::select("year","ccode", "tpop") %>%
  filter(1972<year & year<1980 & ccode!=2) %>%
  left_join(states_70s_year, by = c("year"="year","ccode" = "cow_ccode")) %>%
  mutate(tpop=1000*tpop) %>%
  group_by(ccode,cow_statename) %>%
  summarise(mean_tpop=mean(tpop, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(mean_tpop)) %>%
  mutate(mean_tpop_rank=row_number(),
         cow_statename= replace(cow_statename, cow_statename=="Russia", "Soviet Union")) #Replace "Russia" with "Soviet Union"

table_tag_state_top20<-
  table_tag_state_top20 %>%
  mutate(tag_rank=row_number())    

table_tag_pop_state_top20_comp<-
  table_tag_state_top20 %>%
  left_join(pop_c, by="cow_statename") %>%
  dplyr::select("cow_statename","tag_rank","mean_tpop_rank")

stargazer(table_tag_pop_state_top20_comp,
          summary = FALSE,
          rownames = FALSE,
          type = "text", 
          title="Country TAG Traffic vs. Population", 
          out="./data_analysis_output/table_tag_pop_state_top20_comp.txt",
          covariate.labels=c("Top 20 Countries in Country TAG Traffic", "Rank in Country TAG Traffic", "Rank in Mean Population"))

#stargazer(table_tag_pop_state_top20_comp,
#          summary = FALSE,
#          rownames = FALSE,
#          type = "html", 
#          title="Country TAG Traffic vs. Population", 
#          out="./data_analysis_output/table_tag_pop_state_top20_comp.html",
#          covariate.labels=c("Top 20 Countries<br>in Country TAG Traffic", "Rank<br>in Country TAG Traffic", #"Rank<br>in Mean Population"))
```

country_tag_doc2$cow_statename[country_tag_doc2$cow_statename %in% setdiff(cable_n_all_states$cow_statename, cable_n_states_70s$cow_statename)]

setdiff(cable_n_all_states$cow_statename, cable_n_states_70s$cow_statename)


